Large-scale text pre-training helps with dialogue act recognition, but not without fine-tuning

### 2021-05-07 reports/IWCS2021/iwcs-short-paper.tex
update refs and add SotA

We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), 
which is a subset of the larger Switchboard corpus, 
and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we cluster into a smaller set of 42 tags.
AMI uses a smaller tagset of 16 dialogue acts \citep{GuidelinesDialogueAct2005}.
See Table~\ref{tab:corpora} for details.

@@

\begin{table}[]
\begin{tabular}{@{}lrrrr@{}}
\toprule
           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
\texttt{BERT-FT}    & 36.75                  & 76.60                    & 43.42                  & 64.93                    \\
\texttt{BERT+ID-FT} & 43.63                  & 77.01                    & 46.70                  & \textbf{68.88}           \\
\texttt{BERT+CC-FT} & \textbf{47.78}         & \textbf{77.35}           & \textbf{48.86}         & 68.79                    \\ 
\texttt{BERT+OS-FT} & 41.42                  & 76.95                    & 48.65                  & 68.07                    \\ \midrule
\texttt{BERT-FZ}    &  7.75                  & 55.61           & 14.86                  & 48.34                    \\
\texttt{BERT+ID-FZ} &  6.46                  & 52.30                    & 14.48                  & 48.18                    \\
\texttt{BERT+CC-FZ} &  5.76                  & 51.14                    & 11.34                  & 40.48                    \\ 
\texttt{BERT+OS-FZ} &  \textbf{9.60}         & \textbf{57.67}           & \textbf{17.03}         & \textbf{51.03}           \\ \midrule
\texttt{BERT-RI} & 32.18           & 73.80                    & 34.88                  & 60.89                    \\ \midrule
    Majority class  & 0.78                   & 33.56                    &  1.88                  & 28.27      \\ \bottomrule
\end{tabular}
\caption{Comparison of macro-F1 and accuracy with further in-domain (\texttt{ID}), cross-domain corpus (\texttt{CC}), and OpenSubtitles (\texttt{OS}) dialogue pre-training,
for the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions. \texttt{BERT-RI} uses a randomly initialized utterance encoder with no pre-training but with fine-tuning.}
  \label{tab:results}
\end{table}

>>>>

We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), 
which is a subset of the larger Switchboard corpus, 
and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we cluster into a smaller set of 42 tags.
AMI uses a smaller tagset of 16 dialogue acts \citep{Carletta2007}.
See Table~\ref{tab:corpora} for details.

@@

\begin{table}[]
\begin{tabular}{@{}lrrrr@{}}
\toprule
           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
\texttt{BERT-FT}    & 36.75                  & 76.60                    & 43.42                  & 64.93                    \\
\texttt{BERT+ID-FT} & 43.63                  & 77.01                    & 46.70                  & \textbf{68.88}           \\
\texttt{BERT+CC-FT} & \textbf{47.78}         & \textbf{77.35}           & \textbf{48.86}         & 68.79                    \\ 
\texttt{BERT+OS-FT} & 41.42                  & 76.95                    & 48.65                  & 68.07                    \\ \midrule
\texttt{BERT-FZ}    &  7.75                  & 55.61           & 14.86                  & 48.34                    \\
\texttt{BERT+ID-FZ} &  6.46                  & 52.30                    & 14.48                  & 48.18                    \\
\texttt{BERT+CC-FZ} &  5.76                  & 51.14                    & 11.34                  & 40.48                    \\ 
\texttt{BERT+OS-FZ} &  \textbf{9.60}         & \textbf{57.67}           & \textbf{17.03}         & \textbf{51.03}           \\ \midrule
\texttt{BERT-RI} & 32.18           & 73.80                    & 34.88                  & 60.89                    \\ \midrule
    Majority class  & 0.78                   & 33.56                    &  1.88                  & 28.27      \\ 
    SotA            &    -                   & 83.1\footnotemark                     &     -                  &     -      \\ \bottomrule
\end{tabular}
\caption{Comparison of macro-F1 and accuracy with further in-domain (\texttt{ID}), cross-domain corpus (\texttt{CC}), and OpenSubtitles (\texttt{OS}) dialogue pre-training,
for the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions. \texttt{BERT-RI} uses a randomly initialized utterance encoder with no pre-training but with fine-tuning.}
  \label{tab:results}
\end{table}

\footnotetext{\citet{Ravi2018}} % Not sure whether I really trust this SotA. I doesn't even use dialogue context as far as I can tell and this person https://github.com/glicerico/SGNN says they tried to replicate it and could only get %71.3 accuracy.
